{\bf {\Large Improving estimates of ecosystem metabolism by reducing effects of tidal advection on dissolved oxygen time series}}

### 2015-05-19 review_response.Rnw

6) It would be beneficial to readers if the code for the analysis was distributed with the published paper.

{\it we created a simple R package on GitHub that provides code and examples for implementing weighted regression and estimating ecosystem metabolism. A link was added as supplementary information: \href{https://github.com/fawda123/WtRegDO}{https://github.com/fawda123/WtRegDO}}

\Bigtxt{Reviewer 2:}

Do the authors plan to make their R code available? They mention several times how useful it could be to others (a point on which I certainly agree), but it won’t be useful unless it’s available!

{\it We agree!  We've added a link in the supplementary information that provides instructions and examples for installing a simple R package to implement weighted regression: \href{https://github.com/fawda123/WtRegDO}{https://github.com/fawda123/WtRegDO}}

@@

General comments:

(1) The new method offers significant advantages for the types of systems in the NERRS network, which are the focus of their study. The authors touch on this distinction briefly in lines 98-100, but I think they need to expand on the point and make it more prominent.

{\it Text was added to elaborate this point, both in the introduction and the abstract.

Line 100: `This approach offers a distinct advantage for estuaries where the magnitude of tidal effects on water quality observations can be severe. The weighted regression approach targets the tidal component as a specific parameter during model fitting, which allows the ability to isolate the biological component of the dissolved oxygen time series.  As a result, the weighted regression approach can preserve the true biological signal in the output rather'

Abstract, line

### 2015-05-19 review_response.tex

6) It would be beneficial to readers if the code for the analysis was distributed with the published paper.

{\it we created a simple R package on GitHub that provides code and examples for implementing weighted regression and estimating ecosystem metabolism. A link was added as supplementary information: \href{https://github.com/fawda123/WtRegDO}{https://github.com/fawda123/WtRegDO}}

\Bigtxt{Reviewer 2:}

Do the authors plan to make their R code available? They mention several times how useful it could be to others (a point on which I certainly agree), but it wont be useful unless its available!

{\it We agree!  We've added a link in the supplementary information that provides instructions and examples for installing a simple R package to implement weighted regression: \href{https://github.com/fawda123/WtRegDO}{https://github.com/fawda123/WtRegDO}}

### 2015-05-19 multimedia.tex
all multimedia apps are now on shinyapps

The supporting information for this manuscript includes a graphical illustration of the weighting scheme described in the material and procedures section (\href{http://spark.rstudio.com/beckmw/weights_widget}{http://spark.rstudio.com/beckmw/weights\_widget}), results for each simulation (\href{http://spark.rstudio.com/beckmw/detiding_sims}{http://spark.rstudio.com/beckmw/detiding\_sims}), and results for each case study (\href{http://spark.rstudio.com/beckmw/detiding_cases}{http://spark.rstudio.com/beckmw/detiding\_cases}).  Each link is a graphical summary of data based on interactive inputs to support the results in the manuscript.

>>>>

The supporting information for this manuscript includes a graphical illustration of the weighting scheme described in the material and procedures section (\href{https://beckmw.shinyapps.io/weights_widget}{https://beckmw.shinyapps.io/weights\_widget}), results for each simulation (\href{https://beckmw.shinyapps.io/detiding_sims/}{https://beckmw.shinyapps.io/detiding\_sims/}), and results for each case study (\href{https://beckmw.shinyapps.io/detiding_cases/}{https://beckmw.shinyapps.io/detiding\_cases/}).  Each link is a graphical summary of data based on interactive inputs to support the results in the manuscript.

A simple R package with a sample dataset and code to implement weighted regression is also available on GitHub, including functions to estimate ecosystem metabolism.  See the README file on the web page for download instructions and examples (\href{https://github.com/fawda123/WtRegDO}{https://github.com/fawda123/WtRegDO}).
